### 2017-12-05 Maths Notes/M2/Collisions/Collisions.tex
Notes Update

>>>>

\underline{\huge Collisions example - Oblique Impact}
\includegraphics[width=1.5in]{oblique.png}\\
\textit{A small smooth ball B, moving on a horizontal plane, collides with a fixed vertical wall.\\
Immediately before the collision the angle between the direction of motion of B and the wall is $2\theta$ where $0\degree < \theta < 45\degree$. Immediately after the collision the angle between the direction of motion
of B and the wall is $\theta$ as shown in the diagram above. Given that the coefficient of restitution
between B and the wall is $\frac{3}{8}$ , find the value of $\tan\theta$.}\\
\textbf{Conservation of momentum}\\
\textcolor{red}{$m_1u_1=m_1v_1\Rightarrow u_1=v_1$}\\
$u\cos2\theta=v\cos\theta$\\
$\dfrac{3}{8}=\dfrac{v\sin\theta}{u\sin2\theta}$\\
$3u\sin2\theta=8v\sin\theta$\\
\textbf{Combine result from Conservation of Momentum and Restitution}
